\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/main.tex
Revised abstract

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It \textit{synthesizes} a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript. It also \textit{automatically} extracts
semantics based on rule-based compilations. Each \textit{compile rule}
describes how to convert each abstract algorithm written in a structured natural language
into functions written in \( \ires \), an Intermediate Representation
for ECMAScript. \( \tool \) successfully synthesizes
parsers and compiles 91.60\% of algorithm steps for five recent
ECMAScript versions. We tested the extracted semantics from the next version
ECMAScript 2020 using Test262, the official ECMAScript conformance test
suite. It passed 19,220 of 19,282 tests and we found three specification errors
using our tool. Moreover, we check the adaptability of \( \tool \)
via a case study for an incomplete proposal.
\end{abstract}

>>>>

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It \textit{synthesizes} a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript. It also \textit{automatically} extracts
semantics using rule-based compilation. Each \textit{compile rule}
describes how to convert each abstract algorithm written in a structured natural language
into functions written in \( \ires \), an Intermediate Representation
for ECMAScript. \( \tool \) synthesizes parsers from all \( \bnfes \) productions
and extracts semantics from 91.60\% of algorithm steps for five recent
ECMAScript versions. We manually extend one of the extracted semantics for
the next version of ECMAScript 2020. It passed 19,220 of 19,282 applicable tests
in Test262, the official ECMAScript conformance test suite. While extracting
the semantics using \( \tool \), we found three specification errors
and all of them are confirmed by TC 39. Moreover, we succeed to apply
our tool into an incomplete proposal as a case study.
\end{abstract}

### 2019-08-24 icse20/overview.tex
Revised abstract

In this section, we introduce the overall structure of \( \tool \)
depicted in Figure~\ref{fig:overview} and the outline of the paper.
Compared to the existing approaches shown in
Figure~\ref{fig:existing}, \( \tool \) automatically generates
{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} from the
ECMAScript specification.  Inside \( \tool \), {\sf Spec Extractor}
extracts the JavaScript syntax to build the parser and its semantics
to build the translator.

The motivation of automatically extracting syntax and semantics
of JavaScript from the ECMAScript specification is twofold: 1) the
natural language used in the specification follows well-organized
specific patterns, and 2) the specification is available as HTML files
using various HTML tags.  As the first step, we developed {\sf Spec Extractor}
in JavaScript, which extracts the syntax and semantics from the
ECMAScript specification in HTML into JSON format.

>>>>

In this section, we introduce the overall structure of \( \tool \)
depicted in Figure~\ref{fig:overview} and the outline of the paper.
Compared to the existing approaches shown in
Figure~\ref{fig:existing}, \( \tool \) automatically generates
{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} from the
ECMAScript specification.

The motivation of automatically extracting syntax and semantics
of JavaScript from the ECMAScript specification is twofold: 1) the
natural language used in the specification follows well-organized
specific patterns, and 2) the specification is available as HTML files
using various HTML tags.  As the first step, we developed {\sf Spec Extractor}
to simply collect and save both syntax and semantics into JSON format.
It is written in JavaScript because the ECMAScript specifications are
provided as HTML files.
